\cvsection{Experiences}
\begin{cventries}
	\cventry
	{Senior Machine Learning Engineer, Motion Control Center}
	{XPeng Robotics}
	{Jan. 2022 - Present}
	% {Santa Clara, California}
	{}
	{
		\begin{cvitems}
			\item {
				\textbf{Innovation} Led biomimetic gait controller projects using reinforcement learning, surpassing state-of-the-art (SOTA) methods in all metrics, including 1.5x enhanced disturbance rejection and doubled maximum velocity, with successful adaptation to new rough terrains and tasks. Two patents pending.
			}
			\item {
				\textbf{Locomotion} Developed a quadruped robot locomotion controller combining reinforcement learning with model-based control, achieving state-of-the-art disturbance rejection.
			}
			\item {
				\textbf{Optimization} Devised an analytical method to iterate reinforcement learning reward function, cutting model iterations by up to 70\%.
			}
			\item {
				\textbf{Infrastructure} Overhauled the reinforcement learning pipeline with a modular approach, reduced manual tasks by 80\%.
			}
			\item {
				\textbf{Strategy} Examined state-of-the-art machine learning techniques for quadruped control, large language models, manipulators, and embodied AI, offering strategic insights for departmental product development.
			}
		\end{cvitems}
	}
	\cventry
	{Developer, Master Thesis}
	{Autonomous System and Biomechatronics Lab}
	% {Toronto, Ontario}
	{Sep. 2018 - Aug. 2021}
	{}
	{
		\begin{cvitems}
			\item {
				\textbf{Deep Learning} Directed and \textbf{published} a novel sim-to-real pipeline  in Pytorch for end-to-end reinforcement learning in rough terrain navigation, achieving an 87\% real world and 90\% simulation success rate, marking a 72\% improvement over against benchmarks.
			}
			% \item {
			% 	\textbf{Sim-to-Real} Researched, designed, and implemented a high fidelity Gazebo simulator and domain randomization
			% }
			\item {
				\textbf{Development} Created a distributed robot system using ROS, C++, Python, and SolidWorks, encompassing a simulator, LiDAR and VIO SLAM, position controller, hardware driver, reinforcement learning framework, 3D reconstruction, sensor interfaces, and teleoperator.
			}
			% \item {
			% 	\textbf{Localization} Implemented LiDAR and visual SLAM on a mobile robot for real time pose estimation
			% }
			% \item {
			% 	\textbf{Control} Designed and optimized a cascade PID controller for global position and wheel control in rough terrain
			% }
			\item {
				\textbf{Analysis} Conducted real-world navigation, comparison, and ablation studies, proving the pipeline's efficacy with an 87\% real-world success rate from a 90\% simulation success rate, representing up to a 72\% improvement over existing methods.
			}
			% \item {
			% 	\textbf{Hardware} Enhanced a robot with auxilliary computing units and sensors with components designed using SolidWorks
			% }
			\item {
				\textbf{Publication} Published in \href{https://ieeexplore.ieee.org/document/9468918}{1) IEEE Robotics and Automation Letters 2021 and 2) IROS 2021 Conference}.
			}
		\end{cvitems}
	}
	\cventry
	{Developer, Autonomous Driving Division}
	{Huawei Noah’s Ark Lab}
	% {Toronto, Ontario}
	{May. 2020 - Jan 2021}
	{}
	{
		\begin{cvitems}
			\item {
				\textbf{Path Planning} Developed, \textbf{published}, and \textbf{patented} an innovative Delaunay Triangulation-based algorithm for mapless autonomous vehicle navigation in dynamic settings, resulting in an 18\% improvement in navigation success and a 28\% rise in valid planning compared to conventional methods.
			}
			% \item {
			% 	\textbf{Development} Implemented a Python based path planning simulator and the algorithm's modules for fast development iterations
			% }
			% \item {
			% 	\textbf{Algorithms} Implemented Hybrid A* and Funnel algorithm for path planning in triangulation mesh
			% }
			\item {
				\textbf{Simulation} Involved in based CARLA simulator development for automating the map generation process using real-world datasets.
			}
			\item{
				\textbf{Publications} Published in 1) \href{https://ieeexplore.ieee.org/document/9636067}{IROS 2021 Conference} and 2) \href{https://patents.google.com/patent/US20220135068A1/en}{US Patent Application No. 17/515,522}.
			}
		\end{cvitems}
	}
	% \cventry
	% {Head Teaching Assistent}
	% {MIE443 Mechatronics Systems: Design \& Integration}
	% % {Toronto, Ontario}
	% {Jan. 2018 - Apr. 2020}
	% {}
	% {
	% 	\begin{cvitems}
	% 		\item {
	% 			\textbf{Lecture} Lectured 4th year engineering students on ROS based robot navigation and SLAM methods
	% 		}
	% 		\item {
	% 			\textbf{Mentorship} Guided students on ROS based autonomous robot algorithm development, vision sensor, and OpenCV
	% 		}
	% 		\item \textbf{\href{https://www.mie.utoronto.ca/congratulations-2019-20-teaching-assistant-award-winners-lap-tak-chu-richard-hu-behzad-khamidehi-ben-leung-and-khalil-sidawi/}{Award}} Recipient of UofT MIE 2019-20 Teaching Assistant Award
	% 	\end{cvitems}
	% }
	% \cventry
	% {Developer, Pico-Scale Hydro Turbine Design}
	% {Water and Energy Research Laboratory}
	% % {Toronto, Ontario}
	% {Jan. 2018 - Sep. 2018}
	% {}
	% {
	% 	\begin{cvitems}
	% 		\item {\textbf{Mechanical} Designed and published a variable guide vane for pico-scale hydro turbine using SolidWorks}
	% 		\item {\textbf{Analysis} Evaluated the guide vane failure mode with fluid pressure test, mechanical stress test, and finite element analysis}
	% 		\item {\textbf{Development} Prototyped the turbine and an experiment pipeline using Arduino, SLA 3D printing and machining techniques}
	% 	\end{cvitems}
	% }
	% \cventry
	% {Mechanical Engineer Intern, Novasight Hybrid System}
	% {Conavi Medical} 
	% % {Toronto, Ontario}
	% {May. 2016 - Aug. 2017}
	% {}
	% {
	% 	\begin{cvitems}
	% 		\item {
	% 			\textbf{Analysis} Investigated potential design hazards and risks of catheter rotary assembly
	% 		}
	% 		\item {
	% 			\textbf{Manufacturing} Streamlined an efficient assembly and calibration work instruction for intravascular catheter}
	% 		\item {
	% 			\textbf{Organization} Established an inventory system with full traceability for FDA 510k submission validation}
	% 		\item {
	% 			\textbf{Management} Directed technical design reviews with senior leadership, accelerated the exit of the project phase}
	% 		\item {
	% 			\textbf{Mechanical} Designed imaging and rotary assembly for a intravascular catheter using MATLAB and SolidWorks
	% 		}
	% 	\end{cvitems}
	% }
	% \cventry
	% {Researcher}
	% {Multiphase Flow and Spray Systems Lab} 
	% % {Toronto, Ontario}
	% {Jun. 2015 - Sep. 2015}
	% {}
	% {
	% 	\begin{cvitems}
	% 		\item {
	% 			\textbf{Development} Developed Arduino based camera to fluid pipeline synchronization system to speed up data collection by 85\%
	% 		}
	% 		\item {
	% 			\textbf{Analysis} Classified 13 novel air-fluid impingement shatter pattern using statistical analysis}
	% 	\end{cvitems}
	% }  
\end{cventries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Other Experiences
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
