\cvsection{Projects}
\begin{cventries}
	% \cventry
	% {Personal Project}
	% {\href{https://github.com/rhklite/Parallel-PPO-PyTorch}{Parallel Proximal Policy Gradient in Pytorch}}
	% % {Toronto, Ontario}
	% {Nov. 2019}
	% {}
	% {
	% 	\begin{cvitems}
	% 		\item {\textbf{Development} Implemented parallel agent for faster experience collection and training for proximal policy gradient in Pytorch}
	% 	\end{cvitems}
	% }
	% \cventry
	% {Developer, Course Project}
	% {\href{https://github.com/rhklite/apprenticeship_inverse_RL}{Apprenticeship Learning with Inverse Reinforcement Learning Implementation}}
	% % {Toronto, Ontario}
	% {Mar. 2019}
	% {}
	% {
	% 	\begin{cvitems}
	% 		\item {\textbf{Development} {Implemented the Apprenticeship Learning algorithm using traditional Q-Learning algorithm in Python}}
	% 		\item {\textbf{Lecture} {Lectured students on the algorithm using a version implemented in Google Colab}}
	% 	\end{cvitems}
	% }
	\cventry
	{Planning and Control Team Member, University of Toronto Team}
	{aUToronto - SAE AutoDrive Challenge (Winner 2018-19)}
	% {Toronto, Ontario}
	{Sep. 2018 - Oct. 2019}
	{}
	{
		\begin{cvitems}
			\item {\textbf{Collaboration} Aim to develop a level 4 autonomous vehicle using ROS and C++ in a team of 30+ students}
			\item {\textbf{Localization} Implemented real-time kinematics GPS using NovAtel's SPAN for centermeter level localization
			}
			% \item {\textbf{Control} Optimized trajectory planner for real time performance		
			% }
			% \item {\textbf{Simulation} Evaluated of planning and control system using kinematics and dynamics model
			% }
			\item {\textbf{Mapping} Automated the semantic map layer's lane to centerline association process using Python, QGIS, and Open Street Map}
		\end{cvitems}
	}
	\cventry
	{Developer, Course Project}
	{\href{https://github.com/rhklite/traffic_accident_prediction}{Toward Smart Cities: Road Accident Prevention}}
	% {Toronto, Ontario}
	{Sep. 2018 - Dec. 2018}
	{}
	{
		\begin{cvitems}
			\item {\textbf{Collaboration} Data-driven accident prediction using Scikit-learn in Python; within a team of 5 students}
			\item {\textbf{Data Engineering} Data collection, visualization, feature engineering, and negative sampling}
			\item {\textbf{Machine Learning} Trained and benchmarked 3 supervised learning models: Random Forest, SVM, and MLP Network}
		\end{cvitems}
	}
	\cventry
	{Developer, Course Project}
	{Autonomous Turtlebot}
	% {Toronto, Ontario}
	{Jan. 2018 - Sep. 2018}
	{}
	{
		\begin{cvitems}
			\item {\textbf{Path Planning} Developed robot coverage and exploration algorithm using ROS and C++}
			\item {\textbf{Computer Vision} Object detection and identification using OpenCV library}
			\item {\textbf{Control} Implemented person-following and emotional model for human-robot interaction}
		\end{cvitems}
	}
	\cventry
	{Developer, Course Project}
	{Autonomous Maze Navigation Rover Design}
	% {Toronto, Ontario}
	{Sep. 2017 - Dec. 2017}
	{}
	{
		\begin{cvitems}
			\item { \textbf{Development} Designed the software and hardware architecture for autonomous payload pick-up and delivery robot in a maze}
			\item { \textbf{Path Planning} Designed and implemented localization, collision avoidance, and path planning algorithm in MATLAB and Arduino}
		\end{cvitems}
	}
	\cventry
	{Mechanical Designer}
	{Open Architecture Quadcopter Design}
	% {Toronto, Ontario}
	{Sep. 2017 - Apr. 2018}
	{}
	{
		\begin{cvitems}
			\item {\textbf{Mechanical} Designed mechanical features of quadcopter using SolidWorks and prototyped using 3D printer}
			\item {\textbf{Analysis} Evaluated failure mode of designed components using ANSYS Explicit Dynamics Analysis}
		\end{cvitems}
	}
\end{cventries}
