%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------

\cvsection{Publications}

%---------------------------------------------------------
% \cvpublicationentry{<publisher>}{<title>}{<authors>}{<detail of publisher>}{<date>}{<link>}

\begin{cventries}
  \cvpublicationentrysimple
    {\href{https://ieeexplore.ieee.org/document/9468918}{A Sim-to-Real Pipeline for Deep Reinforcement Learning Autonomous Navigation in Cluttered Rough Terrain}} % Title
    {\textbf{Hu. H}, Kaicheng Zhang, Aaron Hao Tan, Michael Ruan, Christopher Agia, and Goldie Nejat \hspace*{0pt}\hfill \entrylocationstyle{RAL and IROS2021}} % Authors
    % Authors
    {
    \begin{cvitems}
      \item{Devised a pipeline for transferring complex rough terrain navigation policies from simulation to real-world applications, utilizing high-fidelity simulation, abstract observation space, and domain randomization.
      }
      \item{
        The pipeline achieved an 87\% real-world navigation success rate, based on a 90\% success rate in simulation.
			}
      \item{
				The pipeline has up to a 72\% increase in navigation success compared to existing methods, along with faster travel times and shorter distances.
      }
      % \item IEEE Robotics and Automation Letters (\textbf{RAL}), vol. 6, no. 4, pp. 6569-6576, Oct. 2021, doi: 10.1109/LRA.2021.3093551.
      % \item Accepted into International Conference on Intelligent Robots and Systems (\textbf{IROS}) 2021
    \end{cvitems}
    }
  \cvpublicationentrysimple
    {\href{https://arxiv.org/abs/2110.14786}{Spatial Constraint Generation for Motion Planning in Dynamic Environments}} % Title
    {\textbf{Hu. H}, Peyman Yadmellat \hspace*{0pt}\hfill \entrylocationstyle{Patent and IROS2021}} % Authors
    {
    \begin{cvitems}
      \item {Proposed using triangulation mesh to generate spatial constraints for long-term mapless path planning in dynamic environments.}
      \item {Resolved the limitations of static triangulation mesh assumption and object masking issues prevalent in existing methods.
      }
      \item {Attained up to an 18\% improvement in navigation success rate and a 28\% increase in valid plans compared to existing methodologies.}
      % \item Accepted into International Conference on Intelligent Robots and Systems (\textbf{IROS}) 2021
      \item \href{https://patents.google.com/patent/US20220135068A1/en}{Patent pending}.
    \end{cvitems}
    }
  \cvpublicationentrysimple
    {\href{https://asmedigitalcollection.asme.org/POWER/proceedings-abstract/POWER2020/83747/V001T08A020/1088386}{Optimization and System Identification of a Variable Pico-Scale Hydro Turbine for Pressure Regulation}} % Title
    {Yu. SM, Ko. Y, \textbf{Hu. H}, Seo. J, and Bilton. AM \hspace*{0pt}\hfill \entrylocationstyle{ASME}} % Authors
    {
    \begin{cvitems}
      \item Engaged in the design and prototyping of the turbine and its experiment rig using SolidWorks, machining, and 3D printing.
      % \item ASME 2020 Power Conference. Virtual, Online. August 4–5, 2020. V001T08A020. ASME. https://doi.org/10.1115/POWER2020-16902
    \end{cvitems}
    }
\end{cventries}



%-------------------------------------------------------------------------------
%	SAMPLES
%-------------------------------------------------------------------------------
% Usage: \cvpublicationentry{<publisher>}{<title>}{<authors>}{<detail of publisher>}{<date>}{<description>}

% \cvsubsection{International Journal}

%---------------------------------------------------------
% \cvsubsection{Conference}

% %---------------------------------------------------------
%   \cvpublicationentry
%     {WWW} % Publisher
%     {The Anatomy of a large-scale Social Search Engine} % Title
%     {Horowitz, Damon and Kamvar, Sepandar D.} % Authors
%     {Proceedings of the 19th International Conference on World Wide Web, pp. 431-440}
%     {2010} % Date(s)
%     {http://dl.acm.org/citation.cfm?doid=1772690.1772735}
% \end{cventries}

% \cvsubsection{Patents}
% % Usage: \cvpatententry{<title>}{<authors>}{<patent no.>}{<date>}{<link>}

% \begin{cventries}
%   \cvpatententry
%   % Edison, Thomas Alva. "Electric lamp." U.S. Patent 223,898, issued January 27, 1880.
%     {Electric lamp} % Title
%     {\textbf{Edison, Thomas}} % Authors
%     {US, 223,898} % patent no.
%     {1880.01.27} % Date(s)
%     {https://www.google.com/patents/us223898}
% \end{cventries}