\cvsection{Experience}
\begin{cventries}
	\cventry
	{Researcher, Master Thesis}
	{Autonomous System and Biomechatronics Lab}
	{Toronto, Ontario}
	{Sep. 2018 - Present}
	{
		\begin{cvitems}
			\item {
				\textbf{Autonomy} Designed a mobile robot platform for urban search and rescue in ROS and C++
			}
			\item {
				\textbf{Machine Learning} Developed a deep reinforcement learning network and virtual-to-real transfer pipeline
			}
			\item {
				\textbf{Localization} Implemented lidar and vision based SLAM for real time pose estimation
			}
			\item {
				\textbf{Control} Optimized a robust motion contoller for rough terrain navigation
			}
			% \item {
			% 	\textbf{Hardware} Installed auxilliary computing units and sensors with mounts designed using SolidWorks
			% }
			\item {
				\textbf{Deployment} In house experimental testing with autonomous point to point navigation
			}
		\end{cvitems}
	}
	\cventry
	{Planning and Control Team}
	{aUToronto - SAE AutoDrive Challenge (2018, 2019 Winner)}
	{Toronto, Ontario}
	{Sept. 2018 - Present}
	{
		\begin{cvitems}
			\item {\textbf{Autonomy} Aim to develop a level 4 autonomous vehicle using ROS and C++; team of 30+ students}
			\item {\textbf{Localization} Implemented real-time kinematics GPS for precision localzation
			}
			\item {\textbf{Planning} Optimize trajectory planner for real time performance		
			}
			\item {\textbf{Simulation} Evaluation of planning and control system using kinematics and dynamics model
			}
			% \item {\textbf{Mapping} Processed semantic map using Python, QGIS and Open Street Map for level 3 autonomy vehicle}
		\end{cvitems}
	}	
	\cventry
	{Course Project}
	{Toward Smart Cities: Road Accident Prevention}
	{Toronto, Ontario}
	{Sep. 2018 - Dec. 2018}
	{
		\begin{cvitems}
			\item {\textbf{Smart City} Data-driven accident prediction using scikit-learn in Python; team of 5 students}
			\item {\textbf{Data Engineering} Data collection, visualization, feature engineering, and negative sampling}
			\item {\textbf{Machine Learning} Trained and benchmarked 3 supervised learning models: Random Forest, SVM, and Deep Neural Network}
		\end{cvitems}
	}
	\cventry
	{Course Project}
	{Autonomous Turtlebot}
	{Toronto, Ontario}
	{Jan. 2018 - Sep. 2018}
	{
		\begin{cvitems}
			\item {\textbf{Mapping} Developed robot coverage and exploration algorithm using ROS and C++}
			\item {\textbf{Computer Vision} Object detection and identification using OpenCV library}
			\item {\textbf{Social} Implemented person-following and emotional model for human-robot interaction}
		\end{cvitems}
	}
	\cventry
	{Course Project}
	{Autonomous Maze Navigation Rover Design}
	{Toronto, Ontario}
	{Sep. 2017 - Dec. 2017}
	{
		\begin{cvitems}
			\item { \textbf{Autonomy} Implemented localization, collision avoidance, and path planning algorithm in MATLAB and Arduino}
			\item { \textbf{Control} Designed architecture for autonomous payload pick-up and delivery in a maze}
		\end{cvitems}
	}
	\cventry
	{Mechanical Engineer Intern}
	{Conavi Medical - Novasight Hybrid System} 
	{Toronto, Ontario}
	{May. 2016 - Aug. 2017}
	{
		\begin{cvitems}
			\item {
				\textbf{Research} Investigated potential design hazards and risks of catheter rotary assembly
			}
			\item {
				\textbf{Manufacturing} Streamlined an efficient assembly and calibration work instruction}
			\item {
				\textbf{Organisation} Established a inventory system with full traceability for FDA 510k submission validation}
			\item {
				\textbf{Project Management} Directed technical design reviews with senior leadership; accelerated the exit of the project phase}
			% \item {
			% 	\textbf{Design} Designed imaging and rotary assembly for a intravascular catheter using MATLAB and SolidWorks
			% }
		\end{cvitems}
	}  
\end{cventries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Other Experiences
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \cventry
% {Teaching Assistent}
% {MIE443 Mechatronics Systems: Design \& Integration}
% {Toronto, Ontario}
% {Jan. 2018 - Apr. 2018}
% {
%   \begin{cvitems}
%     \item {
%       \textbf{Tutorial} Prepared and gave lecture for students on robot navigation and SLAM methods
%     }
%     \item {
%       \textbf{Laboratory} Mentored students during their robot development process
%     }
%   \end{cvitems}
% }
