\cvsection{Projects}
\begin{cventries}
  \cventry
  {Mapping and Localization Team}
  {aUToronto - Autodrive challenge}
  {Toronto, Ontario}
  {Sept. 2018 - July. 2019}
  {
    \begin{cvitems}
      \item {Developped code for processing and parsing semantic map using python, QGIS and Open Street Map}
      \item {Implemented real-time kinematics GPS system on the autonomous vehicle for localzation}
    \end{cvitems}
  }

  \cventry
  {Data Analysist}
  {Toward Smart Cities:Data-driven Road Accident Prevention}
  {Toronto, Ontario}
  {Sept. 2018 - Dec. 2018}
  {
    \begin{cvitems}
      \item {Binary prediction of road accidents using weather, census, traffic, geography data, feature-engineering, and negative sampling}
      \item {Implemented SVM, Random Forest, and Deep Neural Network model, achieving 90\% cross validated accuracy and 67\% recall for collision}
    \end{cvitems}
  }

  \cventry
    {Mechanical Design}
    {Pico-Scale Hydro Turbine Design}
    {Toronto, Ontario}
    {Jan. 2018 - Sept. 2018}
    {
      \begin{cvitems}
        \item {Designed a variable guide vane mechanism for pico-scale hydro turbine using Solidworks and ANSYS CFX}
        \item {Built the pico-scale turbine and pressurized pipeline test rig to mimic operating conditions}
      \end{cvitems}
    }

    \cventry
    {Software Development \& System Design}
    {Autonomous Maze Navigation Rover Design}
    {Toronto, Ontario}
    {Sept. 2017 - Dec. 2017}
    {
      \begin{cvitems}
        \item {Implemented 2D histogram localization, ultrasound obstacle detection, A* path planning algorithm in MATLAB and Arduino}
        \item {Architecture to govern autonomous navigation through a maze, localization, path-finding, payload pick-up and delivery}
      \end{cvitems}
    }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Old Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \cventry
% {Project Manager & Mechanical Designer}
% {Open Architecture Quadcopter Capstone Design}
% {Toronto, Ontario}
% {Sept. 2017 - Apr. 2018}
% {
%   \begin{cvitems}
%     \item {Responsible for project planning, scheduling, member dispute arbitration. Coordinated with client and supervisor to ensure the client interest is well represented}
%     \item {Designed mechanical features of quadcopter using SolidWorks and ANSYS. Prototyped using 3D printer}
%   \end{cvitems}
% }

  % \cventry
  %   {System Design}
  %   {Autonomous Turtlebot Navigation}
  %   {Toronto, Ontario}
  %   {Jan. 2018 - Sept. 2018}
  %   {
  %     \begin{cvitems}
  %       \item {Designed a variable guide vane mechanism for pico-scale hydro turbine using Solidworks and ANSYS CFX}
  %       \item {Built the pico-scale turbine and a test rig}
  %     \end{cvitems}
  %   }

\end{cventries}